Reading Notes

### 2020-05-27 paper.tex
add gartner to read
reading arthi's paper!

\cite{Halls1995}
another older paper. Cavendish lab! Photovoltaic effect - production of electrons/holes under illumination. Molecular semiconductors produce excitons instead of free charges. Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials. (electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth. so an interpenetrating network is shwon in this paper to be ideal.
poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV. spin coating on glass slide. they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
The current vs Voltage graph for the mixture was very different under illumination.
they predict these sort of flexible polymer photodetectors will be useful in medical imaging.
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}

>>>>

\cite{Halls1995}
another older paper. Cavendish lab! Photovoltaic effect - production of electrons/holes under illumination. Molecular semiconductors produce excitons instead of free charges. Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials. (electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth. so an interpenetrating network is shwon in this paper to be ideal.
poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV. spin coating on glass slide. they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
The current vs Voltage graph for the mixture was very different under illumination.
they predict these sort of flexible polymer photodetectors will be useful in medical imaging.

\cite{Gartner2019a}
Somehow didn't add this!
University of delaware. There is a Jankowski/Marsh image in Fig 1!
OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
CG -- chemists might not like them but physicists do
atomistic simulations are good when you already know the chain configuration at a state point. Atomistic FF are still tailored to fit the properties of specific systems. got distracted today... will continue with II.B tomorrow
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
